dendro

### 2017-04-07 analysis/test-bai.Rmd
update

compete <- compete %>% 
  mutate(dn = (perim_mm/1000) /pi)

dd <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(loc=='SJ') %>% 
  filter(id_core!='Fresno')
```

@@

@@

>>>>

# Compute diameter (mm)
compete <- compete %>% 
  mutate(dn_mm = (perim_mm / pi))

# Get only focal trees, and only selected variables 
ft <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  select(id_focal, loc, dn_mm, height_cm)

# Select only SJ trees and 
ft_sj <- ft %>% filter(loc=='SJ')

# get Create a dataframe with core ID
cores <- data.frame(id_cores=colnames(sj))

# Extract replicate and Tree ID from core ID 
cores <- cores %>% 
  mutate(id_focal = as.factor(stringr::str_sub(id_cores, 3,5)),
         id_replica = stringr::str_sub(id_cores, 6,8))

# Create df with diameter and height for each core ID 
diam_cores <- cores %>% inner_join(ft_sj, by='id_focal') %>% 
  select(id_cores, dn_mm)

```{r}
# BAI dplR
baisj <- bai.out(rwl = sj, diam = diam_cores)

@@

# Year
n.vec <- seq_len(nrow(myrwl))

# Series
seq_len(ncol(myrwl))

# Select a ring-width series
dat <- myrwl[[1]] 
# Remove NA
dat2 <- na.omit(dat)

    for (i in seq_len(ncol(rwl))) {
        dat <- rwl[[i]]
        dat2 <- na.omit(dat)
        if (is.null(diam)) 
            d <- sum(dat2) * 2
        else d <- diam.vec[i]
        r0 <- d/2 - c(0, cumsum(rev(dat2)))
        bai <- -pi * rev(diff(r0 * r0))
        na <- attributes(dat2)$na.action
        no.na <- n.vec[!n.vec %in% na]
        out[no.na, i] <- bai
    }
    out

@@

rwl

# Test bai.out 
s1 <- sj[1]
b1 <- bai.out(s1)/100

ggplot(s1, aes(y=SNA0101, x=row.names(s1))) + 
  geom_point() + 
  geom_line(b1, aes(y=SNA0101, x=row.names(b1)))

ggplot(s1, aes(y=SNA0101, x=row.names(b1), group=1)) + geom_line()
